---
title: "What the Package Does"
author: Campbell Thomasson
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the Package Does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753THOM24)
```

# Introduction

This package runs various functions designed in our labs we have worked through all semester.

# Functions

## myquad

Runs the quadratic function x^2 - 5*x + 7 for a given value of x.
```{r}
myquad(5)
```

## scatterhist

Returns a sophisticated scatterplot with histogram for variables in a dataset.
```{r}
scatterhist(fire$DAMAGE,fire$DISTANCE,xlab="DAMAGE",ylab="DISTANCE")
```

## mybin

Creates a framework to run binomial distributions.
```{r}
mybin(iter=1000,n=18, p=0.3)
```

## myclt

Creates a uniform distribution of the central limit theorem, given a set sample size and number of iterations.
```{r}
myclt(n=50,iter=10000)
```

## myboot2

If the sample is of size n then the bootstrap re-sampling will create samples of size n with replacement. The following is a function that will facilitate the bootstrap procedure.
```{r}
sam = c(5,10,15,20,25)
myboot2(iter=10000,x=sam,fun="mean",alpha=0.05,cx=1.5)
```

## ntickets

This function finds the optimal number of tickets for an airline to sell in order to have a full flight (N seats filled), taking into account gamma risk of accidentally overbooking and p probability of a customer who buys a ticket actually showing up to the flight.
```{r}
ntickets(N=400,gamma=0.02,p=0.95)
```

## mymlnorm

This function makes a maximum likelihood function for two parameters.
```{r}
mymlnorm(x=c(10,12,13,15,12,11,10),mu=seq(10,15,length=1000),sig=seq(0.1,4,length=1000),lwd=2,labcex=1)
```

# Data Sets

## fire

A data set collected concerning home damage from fire.
```{r}
fire
```
